Footpath Planning for Example-driven Procedural Road Networks

### 2020-04-08 paper/paper.tex
Report todo
Add metric tables with data

@@

@@

TODO: Include a distribution of the shap similarity of matched building footprints, see Fan et al, page 14

@@

@@

>>>>

% TODO: Figure: Overlapping buildings, OSM-SLU, 1:1
% TODO: Figure: Overlapping buildings, OSM-SLU, 1:n

@@

% TODO: Turning function example figure for a polygon

@@

% TODO: Turning function overlap, example figure with two polygos

@@

\section{Results, Metrics}

% TODO: Table of positional offset statistics
% TODO: Table of completeness statistics
% TODO: Statement on completeness

% TODO: Bar plot positional accuracy
% TODO: Bar plot turning functions

@@

\section{Results, Metrics}

\subsection{Completeness by building area}

\begin{table}[]
\begin{tabular}{lllll}
    & Total number of buildings & Area cover & Number of buildings (\%) & Area cover (\%) \\
    OSM & 102755 & 33105023.32... $m^2$ & 60.17\% & 98.18\% \\
    SLU & 170783 & 33718628.97... $m^2$ & 100.00\% & 100.00\%
\end{tabular}
\end{table}

The area cover of the OSM dataset in relation to the SLU dataset was estimated to 98.18\%.

\subsection{Positional offset statistics}

Building matching statistics:

\begin{table}[]
\begin{tabular}{lllll}
    & 1:0 & 1:1 & 1:n & Total \\
    Match count & 9812 & 81722 & 11221 & 102755
\end{tabular}
\end{table}

% TODO: Bar plot positional accuracy
% TODO: Bar plot turning functions
